\chapter{Commercial applications and future work}
Building Ponster has been an opportunity to research how the computer vision field is
evolving and how other companies and institutions are using augmented reality to
build products and new techniques. 

In this chapter we are going to cite several applications that have served as an
inspiration to research about augmented reality and to build Ponster app. Also, we
are going to describe the future work that can be applied to enhance the app
functionality. 

\section{Commercial applications}
\label{sec:comapps}
Speaking about mobile environments only, there are great commercial applications
that use augmented reality available to the major platforms, iOS and Android. In
this section we are going to review a few applications that have served as an
inspiration to Ponster. 

\begin{description}
\item [SkyGuide] \hfill \\
SkyGuide is an augmented reality app that enables the user to identify and get
information about the constellations that are present in the sky. This app uses the
user location and the gyroscope to get both where the user is located and how he is
moving the device. With this information, the application presents a view that
resembles to the night sky with all the information about the visible
constellations, planets and stars.

\item [IKEA] \hfill \\
The IKEA application also uses Vuforia SDK to bring quality augmented reality
experience to the mobile phone. Using the IKEA catalog as the object to track, users
can throw the catalog to the floor and test how any furniture would look. The size
of the furniture is realistic because they know the exact sizes of the catalog, so
they can easily determine at what size the objects must be rendered.

\item [Sony TV size] \hfill \\
This application enables users to test if a Sony TV is going to fit well in their
living room. They use a custom pattern that the user has to put where they want to
test the virtual television. Again, this application manages to render a real size
TV by using a know-size pattern.

\item [LEGO Connect] \hfill \\
LEGO Connect also uses Vuforia to virtually enhance their product catalog. With a
LEGO product catalog, the user can identify any of the products displayed and draw a
virtual 3D model of any of their toys. These models can also be animated.
\end{description}

\section{Future work}
There are several improvements that can be done to Ponster to enhance the
functionality and user experience of the app. After reviewing the applications
mentioned in the previous section~\ref{sec:comapps}, it is clear that augmented
reality-based applications can improve customer experience when browsing products. 

In this section we are going to review some of the different improvements that can
be implemented in Ponster app.

\subsection{API integration}
Ponster has been developed to be ready to integrate to an external API. From the
model to the design of the controllers or the tracking algorithm, everything is
independent in terms of where the poster data comes from. 

One of the most important improvements that could be made to Ponster is to integrate
it with an REST API to get the poster data. Actually the poster meta-data is attached
when the application starts, and the poster images are embedded inside the
application sandbox. Integrating an API would be easy with the actual state of the
application. We could send a GET request to the API to download the poster meta-data
when the application starts. This meta-data should have the poster information and
the URL of the images, so when the poster gets in the screen we download its
image. 

This API should have three main features: provide a registration process to the
user, enable the user to browse different types of posters or wall-related products
and providing a payment process to purchase posters.

\subsection{Purchasing posters}
Ponster has been built with the goal in mind of allowing users to browse, try and
buy posters directly from the application. The API integration can bring the ability
to get the products and the purchase process.

With the latest iOS API, a new way to make payments has been introduced to the
recent iPhone devices. This new feature is called Apple Pay\cite{applepay} and uses
the TouchID fingerprint sensor and the credit card associated with the Apple ID
account to process the payments.

\subsection{Custom images}
The current version of Ponster supports \texttt{png} images as the poster images
only. One improvement that could be made to the application is to enable users to
choose a poster image from its camera roll.

In order to implement this feature, there should be changes to the navigation and
menus of the app and to the texture load of the augmented reality algorithm. This
could be integrated with an option in the API to enable the user to print their
custom image instead of buying an existing one.

\subsection{Poster image sizes}
When trying a poster, it is very important to represent it with the real size of
it. This version of Ponster do not draws the posters in real size because it is
dependent of the size of the marker chosen by the user, so if a small marker is
chosen, a small version of the poster will be rendered.

One fundamental feature to improve Ponster could be enabling the user to print a
custom marker ---like the catalog of IKEA or the pattern used in the Sony app---
with fixed size in order to render the posters with their real size. This could be
used to improve the buying experience.

Also, we could use this to deliver several sizes to each poster. With this, the user
could try the size that fits better to their needs and also try it knowing that the
size of the poster that is being drawn with is actually the real size.
